State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
more paper edits
adding standard deviations of the parameters

The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}. The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are consistently over the true value (with a mean bias of \dean{??~\%}). The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian, which centred about the true values, with standard deviation \dean{??}.  \dean{ for discussion: indicating good results}. The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}. The distribution of estimates for $\hat\theta_0/\hat\theta_1$ are relativity tighter, though indicate a bias... This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.

>>>>

The distribution of the estimated parameters is shown in Figure~\ref{fig:Parameters}. The estimates for $\xi$, where $\xi=1-\zeta T_s $ and $\zeta$ is the reciprocal of the synaptic time constant, are consistently over the true value (with a mean bias of 2.5~\%). The estimates of the connectivity kernel parameters ($\theta_0$, $\theta_1$, $\theta_2$) form distributions that are approximately Gaussian, which centred about the true values, with standard deviations 2.88, 1.99 and 0.08\parham{(0.0829)} respectively.  \dean{ for discussion: indicating good results}. The ratios of the estimates ($\hat\theta_0/\hat\theta_1$ and $\hat\theta_0/\hat\theta_2$) are shown in Figure~\ref{fig:ParametersRatio}. The distribution of estimates for $\hat\theta_0/\hat\theta_1$ are relativity tighter\parham{(it's 0.0812 (a bit tighter) and 3.757 respectively)}, though indicate a bias... This indicates the balance of excitation and inhibition can be estimated more accurately than the individual parameters.
